Parameter Estimation in Toy Climate Models Utilizing a Genetic Algorithm

### 2013-12-09 project003/UVM/paper/mcrn501-p3.body.tex
set up for final paper

\section{Introduction}

@@

\begin{figure}[tpb!]
\centering
  \includegraphics[width=.48\textwidth]{../data/dO18/d18O_lisiecki_noname.pdf}
  \caption{
    The LR04 benthic $\delta ^{18} O$ stack over the Pleistocene, constructed by the graphic correlation of fifty-seven globally distributed benthic $\delta ^{18} O$ records versus time (data from Lisieki \cite{lisiecki2005pliocene}).
  }
  \label{fig:insol-data}
\end{figure}

@@

\begin{figure}[tpb!]
\centering
  \includegraphics[width=.45\textwidth]{../src/discrete_plot_noname.pdf}
  \caption{
    The discrete Paillard model.
  }
  \label{fig:paillard-fig3}
\end{figure}

@@

\begin{figure}[tpb!]
\centering
  \includegraphics[width=.48\textwidth]{../data/insolation/laskar2004/insol_data2_noname.pdf}
  \caption{
    The average daily solar insolation $\overline{Q}_{\text{day}}$ is computed on the summer solstice at 65N with the prodived $e,\epsilon,$ and $\overline{\omega}$.
  }
  \label{fig:insol-data}
\end{figure}

@@

\begin{figure}[tpb!]
\centering
  \includegraphics[width=.48\textwidth]{cmaes.png}
  \caption{
    A cartoon representing 6 generations in a CMA-ES experiment. Here, lighter colors indicate improved fitness. The dashed lines represent the influence of the covariance matrix.\\
    }
  \label{fig:cmaes}
\end{figure}

@@

\begin{figure}[tpb!]
\centering
  \includegraphics[width=.48\textwidth]{gaImg.png}
  \caption{
      A schematic explaining the basic steps in a genetic algorithm.
    }
  \label{fig:ga}
\end{figure}

@@

\begin{figure}[tpb!]
\centering
  \includegraphics[width=.48\textwidth]{../src/results_plot_noname.pdf}
  \caption{
      The best result from the GA experiments attempting to fit parameters to Paillard's discrete and ODE model, with the \DO data used for fitness.
    }
  \label{fig:results}
\end{figure}

>>>>

section{Introduction}

@@

\begin{figure}[tpb!]
\centering
  \includegraphics[width=.48\textwidth]{figures/d18O_lisiecki_noname.pdf}
  \caption{
    The LR04 benthic $\delta ^{18} O$ stack over the Pleistocene, constructed by the graphic correlation of fifty-seven globally distributed benthic $\delta ^{18} O$ records versus time (data from Lisieki \cite{lisiecki2005pliocene}).
  }
  \label{fig:insol-data}
\end{figure}

@@

\begin{figure}[tpb!]
\centering
  \includegraphics[width=.45\textwidth]{figures/discrete_plot_noname.pdf}
  \caption{
    The discrete Paillard model.
  }
  \label{fig:paillard-fig3}
\end{figure}

@@

\begin{figure}[tpb!]
\centering
  \includegraphics[width=.48\textwidth]{figures/insol_data2_noname.pdf}
  \caption{
    The average daily solar insolation $\overline{Q}_{\text{day}}$ is computed on the summer solstice at 65N with the prodived $e,\epsilon,$ and $\overline{\omega}$.
  }
  \label{fig:insol-data}
\end{figure}

@@

\begin{figure}[tpb!]
\centering
  \includegraphics[width=.48\textwidth]{figures/cmaes.png}
  \caption{
    A cartoon representing 6 generations in a CMA-ES experiment. Here, lighter colors indicate improved fitness. The dashed lines represent the influence of the covariance matrix.\\
    }
  \label{fig:cmaes}
\end{figure}

@@

\begin{figure}[tpb!]
\centering
  \includegraphics[width=.48\textwidth]{figures/gaImg.png}
  \caption{
      A schematic explaining the basic steps in a genetic algorithm.
    }
  \label{fig:ga}
\end{figure}

@@

\begin{figure}[tpb!]
\centering
  \includegraphics[width=.48\textwidth]{figures/results_plot_noname.pdf}
  \caption{
      The best result from the GA experiments attempting to fit parameters to Paillard's discrete and ODE model, with the \DO data used for fitness.
    }
  \label{fig:results}
\end{figure}
